\chapter{User Manual}

\section{Introduction}
This chapter describes how to use the Opsly platform based on the actual application flow. Opsly provides a public landing experience and an authenticated workspace with modules for customer support, marketing automation, campaign operations, finance analytics, document management, chatbot review, and voice bot setup.

\section{User Types}
The platform is organized around two usage modes:
\begin{itemize}
    \item \textbf{Visitor}: can view the landing page, About Us page, and the public chat support trial.
    \item \textbf{Authenticated User}: can access the dashboard modules after signing in or creating an account.
\end{itemize}

\section{Getting Started}
To start using Opsly, follow these steps:
\begin{itemize}
    \item Open the website in a compatible browser.
    \item Review the landing page to understand the available product areas.
    \item Click \textbf{Login} if you already have an account, or click \textbf{Sign Up} to create one.
    \item After successful authentication, you will be redirected to the authenticated workspace.
\end{itemize}

\section{Public Pages}

\subsection{Landing Page}
The landing page is the first page shown to visitors. It introduces the product and provides quick access to the main public actions.
\begin{itemize}
    \item Open the home page of the website.
    \item View the product introduction and feature cards.
    \item Click \textbf{Learn More} to open the About Us page.
    \item Click \textbf{Login} or \textbf{Sign Up} to access the platform.
    \item Click \textbf{Chat Support Trial} to open the public chat experience.
\end{itemize}

\subsection{About Us}
The About Us page explains the purpose of the platform and its major capabilities.
\begin{itemize}
    \item Open the \textbf{About Us} page from the top navigation or from the landing page.
    \item Read the platform mission and feature overview.
    \item Use the call-to-action buttons to move to sign up or chat support.
\end{itemize}

\subsection{Chat Support Trial}
The public chat support page allows visitors to try the support experience without entering the authenticated dashboard.
\begin{itemize}
    \item Click \textbf{Chat Support Trial} from the landing page or About Us page.
    \item Enter a message in the chat interface.
    \item Review the response returned by the support assistant.
\end{itemize}

\section{Authentication}

\subsection{Sign Up}
To create a new account, follow these steps:
\begin{itemize}
    \item Click \textbf{Sign Up} from the landing page.
    \item Enter your full name, email address, password, and confirm password.
    \item Click \textbf{Sign Up} to create the account.
    \item If account creation is successful, the system asks you to verify your email before signing in.
    \item After verification, return to the login page to continue.
\end{itemize}

\subsection{Login}
To log in to Opsly, follow these steps:
\begin{itemize}
    \item Click \textbf{Login} from the landing page.
    \item Enter your email address and password.
    \item Click \textbf{Sign In} to access the workspace.
    \item If credentials are correct, you will be redirected to the dashboard.
    \item You can also use the \textbf{Continue With Google} button for Google-based sign in.
\end{itemize}

\subsection{Logout}
To log out of the platform:
\begin{itemize}
    \item Open the user avatar menu in the top-right corner of the dashboard.
    \item Click \textbf{Sign Out}.
    \item Your session ends and you are redirected to the login page.
\end{itemize}

\section{Dashboard Navigation}
After logging in, the dashboard layout displays a left navigation rail on desktop and a mobile menu on smaller screens. The layout provides access to the following modules:
\begin{itemize}
    \item AI Documents
    \item Customer Support
    \item Social media automation
    \item Campaign Ops
    \item Finance
    \item Chatbot
    \item Voice Bot
\end{itemize}

The top bar also contains the user profile menu, search and notification icons, and a \textbf{Support Us} button.

\section{Dashboard Modules}

\subsection{AI Documents}
The AI Documents page is used to upload and manage knowledge files for AI tools.
\begin{itemize}
    \item Click \textbf{AI Documents} from the left navigation.
    \item Drag and drop files into the upload area or click to browse your device.
    \item Upload one or multiple files at the same time.
    \item View uploaded documents in the list on the right side of the page.
    \item Delete a document if it is no longer needed.
\end{itemize}

\subsection{Customer Support}
The Customer Support module is used to review support tickets and open ticket details.
\begin{itemize}
    \item Click \textbf{Customer Support} from the dashboard navigation.
    \item Review the ticket summary cards and the ticket list.
    \item Click a ticket row to open the ticket detail page.
    \item Use the ticket detail view to inspect the full conversation or status information.
\end{itemize}

\subsection{Social Media Automation}
The marketing module allows users to connect social platforms and publish or schedule posts.
\begin{itemize}
    \item Click \textbf{Social media automation} from the dashboard navigation.
    \item Review connection cards for Facebook, Instagram, and LinkedIn.
    \item Connect the required social account before posting.
    \item Enter a message and optionally attach an image.
    \item Choose whether to post immediately or schedule for later.
    \item Select one or more target platforms and click the publish action.
    \item After posting, the dashboard refreshes analytics for the connected platforms.
\end{itemize}

\subsection{Campaign Ops}
Campaign Ops is the workflow for profile creation, campaign setup, prospect discovery, email draft generation, and reply tracking.
\begin{itemize}
    \item Click \textbf{Campaign Ops} from the dashboard navigation.
    \item Create a business profile by entering company details.
    \item Create a campaign by selecting a profile and defining the target industry, location, and keywords.
    \item Use \textbf{Discover Prospects} to find new prospects for the selected campaign.
    \item Import prospects manually from CSV when needed.
    \item Generate email drafts for the campaign and edit any draft before sending.
    \item Send the email batch and then check replies for the selected campaign.
    \item Open \textbf{Campaign Conversations} to manage reply threads, edit drafts, and send individual messages.
\end{itemize}

\subsection{Campaign Conversations}
The conversation view shows one email thread at a time.
\begin{itemize}
    \item Select a campaign from the list.
    \item Pick a conversation thread from the left panel.
    \item Review the sent email and all replies in the main panel.
    \item Edit the draft subject and body before sending a message.
    \item Use \textbf{Sync Replies} to fetch new responses.
    \item Send the selected email when the draft is ready.
\end{itemize}

\subsection{Finance}
The Finance module is used to manage expense transactions and review financial data.
\begin{itemize}
    \item Click \textbf{Finance} from the dashboard navigation.
    \item View transaction summaries such as total transactions, total expenses, and average expense.
    \item Add a new transaction using the add transaction form.
    \item Upload a CSV file to import multiple transactions at once.
    \item Filter data by year and month.
    \item Open the forecasting, anomaly detection, or reports pages from the finance dashboard.
\end{itemize}

\subsection{Finance Forecast}
The forecast page shows predicted expenses based on historical data.
\begin{itemize}
    \item Open the finance forecast page from the Finance module.
    \item Select the forecast horizon in months.
    \item Review the trend chart and the predicted range.
    \item Use the refresh button to reload the forecast data.
\end{itemize}

\subsection{Finance Anomaly Detection}
The anomaly page shows fraud detection results for stored transactions.
\begin{itemize}
    \item Open the anomaly detection page from the Finance module.
    \item Review the fraud summary cards.
    \item Inspect the transaction table for risk score and fraud labels.
    \item Click \textbf{Refresh} to reload the latest detection history.
\end{itemize}

\subsection{Finance Reports}
The reports page combines charts and export options for financial analysis.
\begin{itemize}
    \item Open the reports page from the Finance module.
    \item Review category, payment method, and trend visualizations.
    \item Export the report as CSV.
    \item Generate a PDF report when a formatted document is needed.
\end{itemize}

\subsection{Chatbot Management}
The chatbot page is used to review chat sessions and their message history.
\begin{itemize}
    \item Click \textbf{Chatbot} from the dashboard navigation.
    \item Select a chat session from the list of customer chats.
    \item Review the conversation transcript in the message viewer.
    \item Use the refresh button to reload available sessions.
\end{itemize}

\subsection{Voice Bot}
The Voice Bot page is used to configure an AI phone assistant and manage supporting resources.
\begin{itemize}
    \item Click \textbf{Voice Bot} from the dashboard navigation.
    \item Create or update the assistant name and system prompt.
    \item Buy or view the voice bot phone number.
    \item Upload documents to support the voice assistant knowledge base.
    \item Review uploaded documents and remove any document that is no longer required.
    \item View call recordings and transcripts from the recordings section.
\end{itemize}

\subsection{Support Us}
The Support Us page is available from the dashboard header.
\begin{itemize}
    \item Click the \textbf{Support Us} button from the top bar.
    \item Scan the displayed QR code using a supported payment app.
    \item Follow the payment instructions to send a contribution.
\end{itemize}

\section{General Notes}
\begin{itemize}
    \item Most dashboard modules require authentication.
    \item Some operations, such as connecting social accounts or sending emails, depend on backend services being available.
    \item If a page displays no data, add the required records first and refresh the page.
    \item The navigation layout adapts to both desktop and mobile screens.
\end{itemize}
